An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards.

### 2023-11-21 article.tex
final draft all is good!!

% for adjusting table width automatically
\usepackage{adjustbox}
\usepackage{tabulary, ragged2e}
\usepackage{booktabs}

@@

\begin{figure} 
  \resizebox{\textwidth}{!}{
  \includegraphics{revenue.pdf}}
  \caption{Decision tree predicting revenue. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:revenue_tree}
 \end{figure}

@@

\begin{figure} 
  \resizebox{\textwidth}{!}{
  \includegraphics{operating_costs.pdf}}
  \caption{A surrogate model decision tree predicting operating costs. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:operating_tree}
 \end{figure}

@@

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{region.pdf}}
  \caption{Decision tree predicting Region. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:region_tree}
 \end{figure}

@@

This study has explored the relationships between vineyard resource use, operations and geographical properties to revenue and operating costs

geographical regions with respect to a vineyards revenue and operating costs. The analysis was based on a large national study of XXX

Three main findings were identified. First, the most important predicted of revenue were XXX

With YYY showing the relationships among the corresponding set of predictor variables

Second XXX for operating cost

Third for regions...

highlight how decisive regional influences can be determining a vineyard's economic outcomes. 

@@

In part some winegrowing strategies are restricted simply through access to water resources, being reflected through the region classification tree (see Figure \ref{fig:region_tree}). Regions are likely to have varying access to different water sources, such as those along the River Murray being able to utilise river water for crops, unlike most coastal regions which may be drawing from surface or underground water sources. Similarly, the connection between region and fuel use is likely an indicator of the level of infrastructure within the region because vineyards in regions without pressurised water will need to use more fuel to pressurise their irrigation systems.

@@

The Table below shows the ranges of each of the continuous variables:
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}lllllllll@{}}
  \toprule
   & count & mean & std & min & 0.25 & 0.5 & 0.75 & max \\ \midrule
  Vineyard Solar & 622 & 22916.89 & 104808 & 1 & 1170.75 & 5500 & 14866.25 & 2300000 \\
  Biodiesel & 25 & 6635.932 & 11768.832104 & 1 & 200 & 500 & 10000 & 37216 \\
  Fungicide Spray & 2260 & 7.724801 & 3.279794 & 1 & 6 & 7 & 9 & 68 \\
  LPG & 958 & 327.831399 & 861.538804 & 1 & 40 & 95.835 & 240 & 11950 \\
  Petrol & 4309 & 825.276809 & 1556.621119 & 1 & 135 & 306.66 & 903 & 38568 \\
  Insecticide Spray & 1092 & 1.707189 & 1.316042 & 0 & 1 & 1 & 2 & 12 \\
  Water Used & 5846 & 7301838 & 558206600 & 0.0007 & 13.2655 & 43 & 146.875 & 42680000000 \\
  Fertiliser & 795 & 91149.89 & 483913.4 & 1 & 560 & 4759.5 & 45148.5 & 11358000 \\
  Diesel & 5585 & 11677.070183 & 24380.588742 & 0.1267 & 1240 & 3850 & 12500 & 591000 \\
  Yield & 5935 & 772.902449 & 2175.113895 & 0.03 & 68 & 192.3 & 601.8795 & 72305 \\
  Herbicide Spray & 2026 & 2.646199 & 2.598899 & 0 & 2 & 2 & 3 & 103 \\
  Slashing & 2290 & 3.311485 & 1.826788 & 1 & 2 & 3 & 4 & 26 \\
  Electricity & 1014 & 58223.07 & 177626.3 & 0.019 & 2160 & 9637 & 36498.25 & 3000000 \\
  Area Harvested & 6049 & 66.52604 & 133.4525 & 2.220446E-16 & 10.13 & 24.5 & 66.8 & 2436.15 \\
  Grape Revenue & 875 & 377972 & 606286.8 & 1 & 76000 & 172964 & 386747 & 5700000 \\
  Operating Costs & 853 & 314187.1 & 511522.6 & 1 & 57315 & 140000 & 327408 & 4482828 \\ \bottomrule
  \end{tabular}
  \end{table}

  \section{Categorical variables}\ref{app: cat_var}
  The tables below describe each possible class a multiclass variable could have taken and the frequency that it occured.
  \subsection{water types}
  % Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  water types & frequency \\ \midrule

@@

  river water and surface water dam and recycled water from other source and mains water & 1 \\ \bottomrule
  \end{tabular}
  \end{table}

\subsection{cover crop types}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  Cover crop types & frequency \\ \midrule
  permanent cover crop volunteer sward & 1822 \\
  permanent cover crop non native & 936 \\
  permanent cover crop native & 490 \\
  annual cover crop & 479 \\
  groundwater and surface water dam & 406 \\
  annual cover crop and permanent cover crop volunteer sward & 309 \\
  bare soil & 225 \\
  permanent cover crop non native and permanent cover crop volunteer sward & 214 \\
  annual cover crop and permanent cover crop non native & 169 \\
  bare soil and permanent cover crop volunteer sward & 129 \\
  bare soil and permanent cover crop non native & 115 \\
  annual cover crop and permanent cover crop non native and permanent cover crop volunteer sward & 101 \\
  bare soil and annual cover crop & 93 \\
  permanent cover crop native and permanent cover crop volunteer sward & 80 \\
  bare soil and permanent cover crop native & 78 \\
  annual cover crop and permanent cover crop native & 78 \\
  permanent cover crop native and permanent cover crop non native & 68 \\
  permanent cover crop native and permanent cover crop non native and permanent cover crop volunteer sward & 44 \\
  annual cover crop and permanent cover crop native and permanent cover crop non native and permanent cover crop volunteer sward & 44 \\
  bare soil and annual cover crop and permanent cover crop volunteer sward & 33 \\
  bare soil and permanent cover crop non native and permanent cover crop volunteer sward & 26 \\
  annual cover crop and permanent cover crop native and permanent cover crop volunteer sward & 17 \\
  bare soil and annual cover crop and permanent cover crop native & 15 \\
  annual cover crop and permanent cover crop native and permanent cover crop non native & 15 \\
  bare soil and annual cover crop and permanent cover crop non native & 13 \\
  bare soil and annual cover crop and permanent cover crop native and permanent cover crop non native and permanent cover crop volunteer sward & 12 \\
  bare soil and annual cover crop and permanent cover crop non native and permanent cover crop volunteer sward & 11 \\
  bare soil and annual cover crop and permanent cover crop native and permanent cover crop non native & 8 \\
  bare soil and permanent cover crop native and permanent cover crop non native & 7 \\
  bare soil and permanent cover crop native and permanent cover crop volunteer sward & 6 \\
  bare soil and permanent cover crop native and permanent cover crop non native and permanent cover crop volunteer sward & 4 \\
  bare soil and annual cover crop and permanent cover crop native and permanent cover crop volunteer sward and & 2 \\ \bottomrule
  \end{tabular}
  \end{table}

\subsection{irrigation type}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  Irrigation type & frequency \\ \midrule
  dripper & 4800 \\
  dripper and non irrigated & 342 \\
  Not listed & 319 \\
  dripper and overhead sprinkler & 201 \\
  dripper and undervine sprinkler & 91 \\
  non irrigated & 65 \\
  undervine sprinkler & 53 \\
  dripper and flood & 53 \\
  overhead sprinkler & 46 \\
  dripper and overhead sprinkler and undervine sprinkler & 28 \\
  overhead sprinkler and undervine sprinkler & 12 \\
  dripper and non irrigated and overhead sprinkler & 11 \\
  flood and undervine sprinkler & 10 \\
  dripper and flood and undervine sprinkler & 7 \\
  dripper and flood and non irrigated and overhead sprinkler and undervine sprinkler & 3 \\
  dripper and flood and overhead sprinkler & 3 \\
  non irrigated and undervine sprinkler & 2 \\
  dripper and flood and non irrigated & 1 \\
  dripper and non irrigated and overhead sprinkler and undervine sprinkler & 1 \\
  flood and & 1 \\ \bottomrule
  \end{tabular}
  \end{table}

  \subsection{irrigation energy type}

  % Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  Irrigation energy type & frequency \\ \midrule
  electricity & 2162 \\
  not listed & 2053 \\
  pressure & 586 \\
  electricity and pressure & 396 \\
  diesel & 254 \\
  diesel and electricity & 227 \\
  electricity and solar & 96 \\
  diesel and electricity and pressure & 90 \\
  diesel and pressure & 74 \\
  solar & 50 \\
  electricity and pressure and solar & 23 \\
  diesel and electricity and solar & 14 \\
  diesel and electricity and pressure and solar & 10 \\
  pressure and solar & 9 \\
  diesel and solar & 4 \\
  diesel and pressure and solar and & 1 \\ \bottomrule
  \end{tabular}
  \end{table}

  \subsection{year}
  % Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  data year id & frequency \\ \midrule
  2021/2022 & 954 \\
  2020/2021 & 860 \\
  2019/2020 & 599 \\
  2012/2013 & 590 \\
  2013/2014 & 549 \\
  2015/2016 & 548 \\
  2014/2015 & 505 \\
  2017/2018 & 493 \\
  2016/2017 & 485 \\
  2018/2019 & 466 \\ \bottomrule
  \end{tabular}
  \end{table}

\subsection{giregion}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  giregion & frequency \\ \midrule
  McLaren Vale & 1195 \\
  Barossa Valley & 584 \\
  Murray Darling & 521 \\
  Riverland & 472 \\
  Adelaide Hills & 454 \\
  Langhorne Creek & 347 \\
  Margaret River & 344 \\
  Coonawarra & 284 \\
  Padthaway & 202 \\
  Wrattonbully & 195 \\
  Clare Valley & 149 \\
  Yarra Valley & 122 \\
  Eden Valley & 92 \\
  Tasmania & 89 \\
  Swan Hill & 83 \\
  Grampians & 73 \\
  Orange & 72 \\
  Hunter Valley & 70 \\
  Bendigo & 53 \\
  Great Southern & 51 \\
  Rutherglen & 41 \\
  Robe & 36 \\
  Tumbarumba & 35 \\
  Mornington Peninsula & 32 \\
  King Valley & 32 \\
  Southern Fleurieu & 30 \\
  Heathcote & 29 \\
  Adelaide Plains & 25 \\
  Currency Creek & 24 \\
   & 23 \\
  Henty & 22 \\
  Canberra District & 21 \\
  Southern Flinders Ranges & 20 \\
  Upper Goulburn & 20 \\
  Mudgee & 20 \\
  Mount Benson & 20 \\
  Other & 19 \\
  Riverina & 18 \\
  Alpine Valleys & 15 \\
  Barossa Zone & 14 \\
  Pemberton & 12 \\
  Mount Gambier & 11 \\
  Blackwood Valley & 10 \\
  Kangaroo Island & 10 \\
  Big Rivers Zone Other & 9 \\
  Geographe & 7 \\
  Cowra & 6 \\
  Gundagai & 5 \\
  Strathbogie Ranges & 5 \\
  Glenrowan & 4 \\
  Geelong & 4 \\
  Swan District & 4 \\
  Goulburn Valley & 3 \\
  Beechworth & 3 \\
  Southern Highlands & 3 \\
  Macedon Ranges & 2 \\
  Pyrenees & 2 \\
  Sunbury & 1 \\ \bottomrule
  \end{tabular}
  \end{table}

>>>>

% for adjusting table width automatically
\usepackage{adjustbox}
\usepackage{tabulary, ragged2e}
\usepackage{booktabs}
\usepackage{longtable}

@@

% \begin{figure} 
%   \resizebox{\textwidth}{!}{
%   \includegraphics{revenue.pdf}}
%   \caption{Decision tree predicting revenue. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:revenue_tree}
%  \end{figure}

@@

% \begin{figure} 
%   \resizebox{\textwidth}{!}{
%   \includegraphics{operating_costs.pdf}}
%   \caption{A surrogate model decision tree predicting operating costs. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:operating_tree}
%  \end{figure}

@@

% \begin{figure}
%   \resizebox{\textwidth}{!}{
%   \includegraphics{region.pdf}}
%   \caption{Decision tree predicting Region. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:region_tree}
%  \end{figure}

@@

This study explored the relationships between vineyard resource use, operations and geographical properties to revenue and operating costs. The analysis was based on a large national study of 6049 samples collected over ten years. Three main findings were identified. First, the most important predictors of revenue and operating costs were fuel, yield and area. Secondly, area and fuel were highly interrelated to other variables (see Figure \ref{fig:operating_costs_sankey} and Figure \ref{fig:revenue_sankey}). Finally, the relative importance of predictor variables for region, differed from Revenue and operating costs, with water use being more prominent than yield. Region was also more prominent than illustrated in the Sankey diagrams due to the relative importance for operating cost and revenue being calculated for individual regions and not all regions together. In its entirety region contributed third most prominently in relative importance to revenue, and was of the most relative importance in determining operating costs.

@@

In part some winegrowing strategies are restricted simply through access to water resources. Regions are likely to have varying access to different water sources, such as those along the River Murray being able to utilise river water for crops, unlike most coastal regions which may be drawing from surface or underground water sources. Similarly, the connection between region and fuel use is likely an indicator of the level of infrastructure within the region because vineyards in regions without pressurised water will need to use more fuel to pressurise their irrigation systems.

@@

Table \ref{tab:cont_vars} below shows the ranges of each of the continuous variables:
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \caption{Summary statistics of continuous variables used in XGBoosted models.}\label{tab:cont_vars}
  \resizebox{\textwidth}{!}{\begin{tabular}{@{}lllllllll@{}}
  \toprule
   & count & mean & std & min & 0.25 & 0.5 & 0.75 & max \\ \midrule
  Vineyard Solar & 622 & 22916.89 & 104808 & 1 & 1170.75 & 5500 & 14866.25 & 2300000 \\
  Biodiesel & 25 & 6635.932 & 11768.832104 & 1 & 200 & 500 & 10000 & 37216 \\
  Fungicide Spray & 2260 & 7.724801 & 3.279794 & 1 & 6 & 7 & 9 & 68 \\
  LPG & 958 & 327.831399 & 861.538804 & 1 & 40 & 95.835 & 240 & 11950 \\
  Petrol & 4309 & 825.276809 & 1556.621119 & 1 & 135 & 306.66 & 903 & 38568 \\
  Insecticide Spray & 1092 & 1.707189 & 1.316042 & 0 & 1 & 1 & 2 & 12 \\
  Water Used & 5846 & 7301838 & 558206600 & 0.0007 & 13.2655 & 43 & 146.875 & 42680000000 \\
  Fertiliser & 795 & 91149.89 & 483913.4 & 1 & 560 & 4759.5 & 45148.5 & 11358000 \\
  Diesel & 5585 & 11677.070183 & 24380.588742 & 0.1267 & 1240 & 3850 & 12500 & 591000 \\
  Yield & 5935 & 772.902449 & 2175.113895 & 0.03 & 68 & 192.3 & 601.8795 & 72305 \\
  Herbicide Spray & 2026 & 2.646199 & 2.598899 & 0 & 2 & 2 & 3 & 103 \\
  Slashing & 2290 & 3.311485 & 1.826788 & 1 & 2 & 3 & 4 & 26 \\
  Electricity & 1014 & 58223.07 & 177626.3 & 0.019 & 2160 & 9637 & 36498.25 & 3000000 \\
  Area Harvested & 6049 & 66.52604 & 133.4525 & 2.220446E-16 & 10.13 & 24.5 & 66.8 & 2436.15 \\
  Grape Revenue & 875 & 377972 & 606286.8 & 1 & 76000 & 172964 & 386747 & 5700000 \\
  Operating Costs & 853 & 314187.1 & 511522.6 & 1 & 57315 & 140000 & 327408 & 4482828 \\ \bottomrule
  \end{tabular}}
  \end{table}
\clearpage

  \section{Categorical Variables}
  The tables below describe each possible class a multiclass variable could have taken and the frequency that it occured.
  \subsection{Water Source Types}
  Table \ref{tab:water_type} below shows the different class types for water sources used by vineyards and their frequency of occurrences.
  % Please add the following required packages to your document preamble:
% \usepackage{booktabs}

\begin{center}
  \begin{longtable}{p{0.5\linewidth} p{.35\linewidth}}
    \caption{Frequency and class types of water types used by vineyards.}\label{tab:water_type} \\

  \hline \textbf{Water types} & \textbf{frequency}\\ \hline 
  \endfirsthead

  \multicolumn{2}{c}%
  {{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
  \hline \textbf{Water types} & \textbf{frequency} \\ \hline 
  \endhead

  \hline \multicolumn{2}{|r|}{{Continued on next page}} \\ \hline
  \endfoot

  \hline \hline
  \endlastfoot

@@

    river water and surface water dam and recycled water from other source and mains water & 1 \\

  \end{longtable}
  \end{center}

  \clearpage
\subsection{Cover Crop Types}
Table \ref{tab:cover_crop} below shows the different cover crop types used together and their frequency.

\begin{center}
  \begin{longtable}{p{0.5\linewidth} p{.35\linewidth}}
    \caption{Frequency and class types of cover crop types used by vineyards.}\label{tab:cover_crop} \\

  \hline \textbf{Cover crop types} & \textbf{frequency}\\ \hline 
  \endfirsthead

  \multicolumn{2}{c}%
  {{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
  \hline \textbf{Cover crop types} & \textbf{frequency} \\ \hline 
  \endhead

  \hline \multicolumn{2}{|r|}{{Continued on next page}} \\ \hline
  \endfoot

  \hline \hline
  \endlastfoot

  Cover crop types & frequency \\
  permanent cover crop volunteer sward & 1822 \\
  permanent cover crop non native & 936 \\
  permanent cover crop native & 490 \\
  annual cover crop & 479 \\
  groundwater and surface water dam & 406 \\
  annual cover crop and permanent cover crop volunteer sward & 309 \\
  bare soil & 225 \\
  permanent cover crop non native and permanent cover crop volunteer sward & 214 \\
  annual cover crop and permanent cover crop non native & 169 \\
  bare soil and permanent cover crop volunteer sward & 129 \\
  bare soil and permanent cover crop non native & 115 \\
  annual cover crop and permanent cover crop non native and permanent cover crop volunteer sward & 101 \\
  bare soil and annual cover crop & 93 \\
  permanent cover crop native and permanent cover crop volunteer sward & 80 \\
  bare soil and permanent cover crop native & 78 \\
  annual cover crop and permanent cover crop native & 78 \\
  permanent cover crop native and permanent cover crop non native & 68 \\
  permanent cover crop native and permanent cover crop non native and permanent cover crop volunteer sward & 44 \\
  annual cover crop and permanent cover crop native and permanent cover crop non native and permanent cover crop volunteer sward & 44 \\
  bare soil and annual cover crop and permanent cover crop volunteer sward & 33 \\
  bare soil and permanent cover crop non native and permanent cover crop volunteer sward & 26 \\
  annual cover crop and permanent cover crop native and permanent cover crop volunteer sward & 17 \\
  bare soil and annual cover crop and permanent cover crop native & 15 \\
  annual cover crop and permanent cover crop native and permanent cover crop non native & 15 \\
  bare soil and annual cover crop and permanent cover crop non native & 13 \\
  bare soil and annual cover crop and permanent cover crop native and permanent cover crop non native and permanent cover crop volunteer sward & 12 \\
  bare soil and annual cover crop and permanent cover crop non native and permanent cover crop volunteer sward & 11 \\
  bare soil and annual cover crop and permanent cover crop native and permanent cover crop non native & 8 \\
  bare soil and permanent cover crop native and permanent cover crop non native & 7 \\
  bare soil and permanent cover crop native and permanent cover crop volunteer sward & 6 \\
  bare soil and permanent cover crop native and permanent cover crop non native and permanent cover crop volunteer sward & 4 \\
  bare soil and annual cover crop and permanent cover crop native and permanent cover crop volunteer sward and & 2 \\
  \end{longtable}
  \end{center}
  \clearpage

\subsection{Irrigation Types}
Below in Table \ref{tab:irig_types} are the frequency and different irrigation types.

\begin{center}
  \begin{longtable}{p{0.5\linewidth} p{.35\linewidth}}
    \caption{Frequency and class types of irrigation types used by vineyards.}\label{tab:irig_types} \\

  \hline \textbf{Irrigation types} & \textbf{frequency}\\ \hline 
  \endfirsthead

  \multicolumn{2}{c}%
  {{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
  \hline \textbf{Irrigation types} & \textbf{frequency} \\ \hline 
  \endhead

  \hline \multicolumn{2}{|r|}{{Continued on next page}} \\ \hline
  \endfoot

  \hline \hline
  \endlastfoot
  Irrigation type & frequency \\
  dripper & 4800 \\
  dripper and non irrigated & 342 \\
  Not listed & 319 \\
  dripper and overhead sprinkler & 201 \\
  dripper and undervine sprinkler & 91 \\
  non irrigated & 65 \\
  undervine sprinkler & 53 \\
  dripper and flood & 53 \\
  overhead sprinkler & 46 \\
  dripper and overhead sprinkler and undervine sprinkler & 28 \\
  overhead sprinkler and undervine sprinkler & 12 \\
  dripper and non irrigated and overhead sprinkler & 11 \\
  flood and undervine sprinkler & 10 \\
  dripper and flood and undervine sprinkler & 7 \\
  dripper and flood and non irrigated and overhead sprinkler and undervine sprinkler & 3 \\
  dripper and flood and overhead sprinkler & 3 \\
  non irrigated and undervine sprinkler & 2 \\
  dripper and flood and non irrigated & 1 \\
  dripper and non irrigated and overhead sprinkler and undervine sprinkler & 1 \\
  flood and & 1 \\
\end{longtable}
\end{center}

  \clearpage

  \subsection{Irrigation Energy Type}
Below, Table \ref{irig_energy} shows the different types of energy used to power vineyards and their frequency.

\begin{center}
  \begin{longtable}{p{0.5\linewidth} p{.35\linewidth}}
    \caption{Frequency and class types of irrigation energy types used by vineyards.}\label{tab:irig_energy}  \\

  \hline \textbf{Irrigation Energy types} & \textbf{frequency}\\ \hline 
  \endfirsthead

  \multicolumn{2}{c}%
  {{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
  \hline \textbf{Irrigation Energy types} & \textbf{frequency} \\ \hline 
  \endhead

  \hline \multicolumn{2}{|r|}{{Continued on next page}} \\ \hline
  \endfoot

  \hline \hline
  \endlastfoot

  Irrigation energy type & frequency \\
  electricity & 2162 \\
  not listed & 2053 \\
  pressure & 586 \\
  electricity and pressure & 396 \\
  diesel & 254 \\
  diesel and electricity & 227 \\
  electricity and solar & 96 \\
  diesel and electricity and pressure & 90 \\
  diesel and pressure & 74 \\
  solar & 50 \\
  electricity and pressure and solar & 23 \\
  diesel and electricity and solar & 14 \\
  diesel and electricity and pressure and solar & 10 \\
  pressure and solar & 9 \\
  diesel and solar & 4 \\
  diesel and pressure and solar and & 1 \\ \bottomrule
\end{longtable}
\end{center}

  \clearpage

  \subsection{Year}
Below in Table \ref{tab:year} is the list of years and the number of sample collected in each.

    \begin{center}
      \begin{longtable}{p{0.5\linewidth} p{.35\linewidth}}
        \caption{Frequency and class types of year}\label{tab:year}  \\

      \hline \textbf{Year } & \textbf{frequency}\\ \hline 
      \endfirsthead

      \multicolumn{2}{c}%
      {{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
      \hline \textbf{Year} & \textbf{frequency} \\ \hline 
      \endhead

      \hline \multicolumn{2}{|r|}{{Continued on next page}} \\ \hline
      \endfoot

      \hline \hline
      \endlastfoot

  Year & frequency \\
  2021/2022 & 954 \\
  2020/2021 & 860 \\
  2019/2020 & 599 \\
  2012/2013 & 590 \\
  2013/2014 & 549 \\
  2015/2016 & 548 \\
  2014/2015 & 505 \\
  2017/2018 & 493 \\
  2016/2017 & 485 \\
  2018/2019 & 466 \\

\end{longtable}
\end{center}

\clearpage

\subsection{Region}
Below in Table \ref{tab:region} are the number of collected samples for each region.
\begin{center}
  \begin{longtable}{p{0.5\linewidth} p{.35\linewidth}}
    \caption{Frequency and class types of regions.}\label{tab:region}  \\

  \hline \textbf{Regions} & \textbf{frequency}\\ \hline 
  \endfirsthead

  \multicolumn{2}{c}%
  {{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
  \hline \textbf{Regions} & \textbf{frequency} \\ \hline 
  \endhead

  \hline \multicolumn{2}{|r|}{{Continued on next page}} \\ \hline
  \endfoot

  \hline \hline
  \endlastfoot

  giregion & frequency \\
  McLaren Vale & 1195 \\
  Barossa Valley & 584 \\
  Murray Darling & 521 \\
  Riverland & 472 \\
  Adelaide Hills & 454 \\
  Langhorne Creek & 347 \\
  Margaret River & 344 \\
  Coonawarra & 284 \\
  Padthaway & 202 \\
  Wrattonbully & 195 \\
  Clare Valley & 149 \\
  Yarra Valley & 122 \\
  Eden Valley & 92 \\
  Tasmania & 89 \\
  Swan Hill & 83 \\
  Grampians & 73 \\
  Orange & 72 \\
  Hunter Valley & 70 \\
  Bendigo & 53 \\
  Great Southern & 51 \\
  Rutherglen & 41 \\
  Robe & 36 \\
  Tumbarumba & 35 \\
  Mornington Peninsula & 32 \\
  King Valley & 32 \\
  Southern Fleurieu & 30 \\
  Heathcote & 29 \\
  Adelaide Plains & 25 \\
  Currency Creek & 24 \\
   & 23 \\
  Henty & 22 \\
  Canberra District & 21 \\
  Southern Flinders Ranges & 20 \\
  Upper Goulburn & 20 \\
  Mudgee & 20 \\
  Mount Benson & 20 \\
  Other & 19 \\
  Riverina & 18 \\
  Alpine Valleys & 15 \\
  Barossa Zone & 14 \\
  Pemberton & 12 \\
  Mount Gambier & 11 \\
  Blackwood Valley & 10 \\
  Kangaroo Island & 10 \\
  Big Rivers Zone Other & 9 \\
  Geographe & 7 \\
  Cowra & 6 \\
  Gundagai & 5 \\
  Strathbogie Ranges & 5 \\
  Glenrowan & 4 \\
  Geelong & 4 \\
  Swan District & 4 \\
  Goulburn Valley & 3 \\
  Beechworth & 3 \\
  Southern Highlands & 3 \\
  Macedon Ranges & 2 \\
  Pyrenees & 2 \\
  Sunbury & 1 \\ \bottomrule
\end{longtable}
\end{center}
\clearpage
